Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-02-02 docs/ACM/paper.tex
Adding description of implementation.

>>>>

\paragraph{On the Implementation of \Taskminer.}
We have implemented all the techniques described in this paper in
LLVM~\cite{Lattner04}.
This decision was motivated by two factors.
First, the possibility to reuse all the infra-structure already
available in LLVM to infer symbolic bounds of integer
expressions~\cite{Mendonca17}.
Second, given the state-of-the-art support that LLVM already provides to the
compilation of OpenMP~\cite{Bertolli14,Martineau16,Samuel16}.
